Synthesizing Symmetric Lenses

### 2018-07-07 papers/SymmetricLenses/main.tex
add new theorem

\subsection{Lens Costs}
Our cost metric is based on the expected amount of information required to
recover a string in one data format from the other. We use the function
$\REntropyOf{\RegexAlt \Given \Lens, \Regex}$ to calculate the expected amount
of information required to recover a string in $\RegexAlt$ from a string in
$\Regex$, synchronized by $\Lens$. We use the function $\LEntropyOf{\Regex
  \Given \Lens, \RegexAlt}$ to calculate the expected amount of information
required to recover a string in $\Regex$ from a string in $\RegexAlt$,
synchronized by $\Lens$.
\begin{center}
  \begin{tabular}{rcl}
    $\REntropyOf{\RegexAlt \Given \IdentityLensOf{\RegexAlt}, \RegexAlt}$
    & =
    & 0\\

    $\REntropyOf{\RegexAlt \Given \DisconnectOf{\Regex}{\RegexAlt}{\String}{\StringAlt}, \Regex}$
    & =
    & \EntropyOf{\RegexAlt}\\

@@

    $\REntropyOf{\PRegexOr{\RegexAlt_1}{\RegexAlt_2}{\ProbabilityAlt} \Given \MergeLOf{\Lens_1}{\Lens_2}, \Regex}$
    & =
    & $\ProbabilityAlt*(\REntropyOf{\RegexAlt \Given \Lens_1, \Regex_1}) + (1-\ProbabilityAlt)*(\REntropyOf{\RegexAlt \Given \Lens_2, \Regex_2})$\\

    $\REntropyOf{\RegexAlt \Given \MergeROf{\Lens_1}{\Lens_2}, \PRegexOr{\Regex_1}{\Regex_2}{\Probability}}$
    & =
    & $\Probability*(\REntropyOf{\RegexAlt \Given \Lens_1, \Regex_1} - \Log_2(\Probability)) + $\\
    &
    & $(1-\Probability)*(\REntropyOf{\RegexAlt \Given \Lens_2, \Regex_2} - \Log_2(1 - \Probability))$\\

    $\REntropyOf{\Regex \Given \InvertOf{\Lens}, \RegexAlt}$
    & =
    & $\LEntropyOf{\Regex \Given \Lens, \RegexAlt}$\\
  \end{tabular}
\end{center}
$\LEntropyOf{\Regex \Given \Lens, \RegexAlt}$ is defined symmetrically.  These
functions calculate the expected number of bits to recover one data format from
a synchronized string in the other format.
The cost of a lens, $c(\Lens \OfType \Regex \Leftrightarrow \RegexAlt) =
\LEntropyOf{\Regex \Given \Lens, \RegexAlt} + \REntropyOf{\RegexAlt \Given
  \Lens, \Regex}$ is the
sum of recovering the left format from the right, and the right from the left.
We have proven theorems demonstrating the calculated entropy corresponds to the
actual conditional entropy to recover the data.\bcp{Again, they should be
  included.}

\begin{theorem}
  Let $\Lens \OfType \Regex \Leftrightarrow \RegexAlt$, where $\Lens$ does not
  include composition, $\Regex$ and $\RegexAlt$ and unambiguous, and neither
  $\Regex$ nor $\RegexAlt$ contain any empty subcomponents.
  \begin{enumerate}
  \item $\REntropyOf{\RegexAlt \Given \Lens, \Regex}$ calculates the expected
    information content of $\SetOf{t \SuchThat t \in \LanguageOf{\RegexAlt}}$,
    given $\SetOf{s \SuchThat s \in \LanguageOf{\Regex} \BooleanAnd
      \Lens.\PutROf{s}{t} = t}$
  \item $\LEntropyOf{\Regex \Given \Lens, \RegexAlt}$ calculates the expected
    information content of $\SetOf{s \SuchThat s \in \LanguageOf{\Regex}}$,
    given $\SetOf{t \SuchThat t \in \LanguageOf{\RegexAlt} \BooleanAnd
      \Lens.\PutLOf{t}{s} = s}$
  \end{enumerate}
\end{theorem}

@@

\subsection{Heuristic Usefulness}
We evaluate the usefulness of (1) our information theoretic metric, and (2) our
termination heuristic.  To this end, we run our program in 3 different modes:\\
\begin{tabulary}{\linewidth}{rL}
  \NoTPOpt{}: & We synthesize lenses using our symmetric synthesis algorithm,
                but users cannot tune when \RXSearch returns using a termination parameter.\\
  \FCOpt{}: &  The first time \GreedySynth finds a lens, it returns that lens.\\
  \NMCCOpt{}: & The lens cluster that contains is identified through \SSOpt{}. \GreedySynth is then called on that pair of SREs. \\
  \NMOpt{}: & Neither \GreedySynth nor \RXSearch have any notion of cost; they
              both merely search for
              any lens that satisfies the specification. 
\end{tabulary}

>>>>

\subsection{Lens Costs}
Our cost metric is based on the expected amount of information required to
recover a string in one data format from the other. We use the function
$\REntropyOf{\RegexAlt \Given \Lens, \Regex}$ to bound the expected amount of
information required to recover a string in $\RegexAlt$ from a string in
$\Regex$, synchronized by $\Lens$. We use the function $\LEntropyOf{\Regex
  \Given \Lens, \RegexAlt}$ to bound the expected amount of information required
to recover a string in $\Regex$ from a string in $\RegexAlt$, synchronized by
$\Lens$.
\begin{center}
  \begin{tabular}{rcl}
    $\REntropyOf{\RegexAlt \Given \IdentityLensOf{\RegexAlt}, \RegexAlt}$
    & =
    & [0,0]\\

    $\REntropyOf{\RegexAlt \Given \DisconnectOf{\Regex}{\RegexAlt}{\String}{\StringAlt}, \Regex}$
    & =
    & [\EntropyOf{\RegexAlt},\EntropyOf{\RegexAlt}]\\

@@

    $\REntropyOf{\RegexAlt \Given \MergeROf{\Lens_1}{\Lens_2}, \PRegexOr{\Regex_1}{\Regex_2}{\Probability}}$
    & =
    & $\Probability*(\REntropyOf{\RegexAlt \Given \Lens_1, \Regex_1}) + (1-\Probability)*(\REntropyOf{\RegexAlt \Given \Lens_2, \Regex_2})$\\

    $\REntropyOf{\PRegexOr{\RegexAlt_1}{\RegexAlt_2}{\ProbabilityAlt} \Given \MergeLOf{\Lens_1}{\Lens_2}, \Regex}$
    & =
    & $\ProbabilityAlt*(\REntropyOf{\RegexAlt \Given \Lens_1, \Regex_1}) + $\\
    &
    & $(1-\ProbabilityAlt)*(\REntropyOf{\RegexAlt \Given \Lens_2, \Regex_2} - \Log_2(1 - \ProbabilityAlt))+$\\
    &
    & $(0, -\Log_2(\ProbabilityAlt)*\ProbabilityAlt -\Log_2(1 - \ProbabilityAlt)*(1-\ProbabilityAlt)]$\\

    $\REntropyOf{\Regex \Given \InvertOf{\Lens}, \RegexAlt}$
    & =
    & $\LEntropyOf{\Regex \Given \Lens, \RegexAlt}$\\
  \end{tabular}
\end{center}
$\LEntropyOf{\Regex \Given \Lens, \RegexAlt}$ is defined symmetrically. These
functions bound the expected number of bits to recover one data format from a
synchronized string in the other format. Notice, we would be able to calculate
the exact entropy, were it not for \MergeL. If $\MergeLOf{\Lens_1}{\Lens_2}
\OfType \Regex \Leftrightarrow
\PRegexOr{\RegexAlt_1}{\RegexAlt_2}{\ProbabilityAlt}$, given a string in $s$, we
need to determine if the synchronized string is in $\Regex$ or $\RegexAlt$.
However, this information content is dependent on the how likely the
synchronized string is to be in $\Regex$ or $\RegexAlt$. In the worst case, the
expected information content to encode this choice is
$-\Log_2(\ProbabilityAlt)*\ProbabilityAlt -\Log_2(1 -
\ProbabilityAlt)*(1-\ProbabilityAlt)$, but the expected information content
could be arbitrarily small.

The cost of a lens, $c(\Lens \OfType \Regex \Leftrightarrow \RegexAlt) =
\MaxOf{\LEntropyOf{\Regex \Given \Lens, \RegexAlt}} +
\MaxOf{\REntropyOf{\RegexAlt \Given \Lens, \Regex}}$ is the maximum sum of
recovering the left format from the right, and the right from the left. We have
proven theorems demonstrating the calculated entropy corresponds to the actual
conditional entropy to recover the data.\bcp{Again, the proofs should be
  included.}

\begin{theorem}
  Let $\Lens \OfType \Regex \Leftrightarrow \RegexAlt$, where $\Lens$ does not
  include composition, $\Regex$ and $\RegexAlt$ and unambiguous, and neither
  $\Regex$ nor $\RegexAlt$ contain any empty subcomponents.
  \begin{enumerate}
  \item $\REntropyOf{\RegexAlt \Given \Lens, \Regex}$ bounds the expected
    information content of $\SetOf{t \SuchThat t \in \LanguageOf{\RegexAlt}}$,
    given $\SetOf{s \SuchThat s \in \LanguageOf{\Regex} \BooleanAnd
      \Lens.\PutROf{s}{t} = t}$
  \item $\LEntropyOf{\Regex \Given \Lens, \RegexAlt}$ bounds the expected
    information content of $\SetOf{s \SuchThat s \in \LanguageOf{\Regex}}$,
    given $\SetOf{t \SuchThat t \in \LanguageOf{\RegexAlt} \BooleanAnd
      \Lens.\PutLOf{t}{s} = s}$
  \end{enumerate}
\end{theorem}

@@

\subsection{The Effect of Our Heuristic}
We evaluate the usefulness of (1) our information theoretic metric, and (2) our
termination heuristic.  To this end, we run our program in 3 different modes:\\
\begin{tabulary}{\linewidth}{rL}
  \NoTPOpt{}: & We synthesize lenses using our symmetric synthesis algorithm,
                but users cannot tune when \RXSearch returns using a termination parameter.\\
  \FCOpt{}: &  The first time \GreedySynth finds a lens, it returns that lens.\\
  \NMCCOpt{}: & The lens cluster that contains is identified through \SSOpt{}. \GreedySynth is then called on that pair of SREs. \\
  \NMOpt{}: & Neither \GreedySynth nor \RXSearch have any notion of cost; they
              both merely search for
              any lens that satisfies the specification. 
\end{tabulary}
